Index measures for oak decline severity using phenotypic descriptors

### 2019-12-12 manuscript/figures.Rmd

```{r descriptor_contributions, fig.height = 5,fig.cap = 'Descriptor importance scores from random forest models for relative contributions to\ndecline index measures. a) Phenotypic decline index (PDI). b) Decline acuteness index (DAI)'}
loadd(descriptor_contribution_plots)

>>>>

```{r descriptor_contributions, fig.height = 6,fig.cap = 'Descriptor importance scores from random forest models for relative contributions to\ndecline index measures. a) Phenotypic decline index (PDI). b) Decline acuteness index (DAI)'}
loadd(descriptor_contribution_plots)

### 2019-12-12 manuscript/manuscript.Rmd

**Live crown ratio** -

@@

**Composite crown volume (m^3^)** - Estimated volume of crown as an paraboloid proportional to the crown condition. Based on the composite crown volumne from @zarnoch2004 but uses crown condition instead of crown density.

@@

$r$ = crown radius (m), $h$ = total height (m), $l$ = lower crown height (m), $c$ = crown condition (%)

@@

$r$ = crown radius (m), $h$ = total height (m), $l$ = lower crown height (m), c = crown condition (%)

@@

$S$ = composite crown surface area (m^2^), $v$ = composite crown volume (m^3^)

@@

$h$ = number of *Agrilus* exit holes, $d$ = diameter at breast height (cm)

>>>>

**Live crown ratio (%)** - percentage of the whole tree height that supports live crown.

@@

**Composite crown volume (m^3^)** - Estimated volume of crown as an paraboloid proportional to the crown condition. Based on the composite crown volumne from @zarnoch2004 but uses crown condition instead of crown density alone.

@@

$r$ = crown radius (m)

@@

@@

@@

$h$ = number of *Agrilus* exit holes
